### 2020-11-17 05_Thesis/THESIS_LaTeX/Chapters/3.tex
min progress

\subsection{Rheology of candidate polymer solutions}
As stated in previous sections, near-field electrospinning requires the control of several parameters to obtain fibers with the desired properties. One of the main parameters are related to the polymer precursor such as molecular weight and its concentration in solution. The evaluation of polymer chain entanglements is an effective way to address the spunability of a polymer-solvent system. [23] Polymer concentration and molecular weight are the main factors in determining the entanglement degree between polymer chains. Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains. As the polymer concentration increases, the chains overlap and become entangled. The concentration at which the entanglement initially takes place is the critical concentration $c^*$. Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement. This rapid change in chain entanglement is translated into a fast increase in the viscoelasticity of the solution. Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity.
\cite{Han2019}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.45]{./Figures/concentrationViscosityPlotExplained.png}
\decoRule
\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Burghelea2020, Gupta2005}}
\label{fig:concentrationViscosityPlotExplained}
\end{figure}

>>>>

\subsection{Rheology of candidate polymer solutions}
As stated in previous sections, near-field electrospinning requires the control of several parameters to obtain fibers with the desired properties. One of the main parameters are related to the polymer precursor such as molecular weight and its concentration in solution. The evaluation of polymer chain entanglements is an effective way to address the spunability of a polymer-solvent system. \cite{Shenoy2005} Polymer concentration and molecular weight are the main factors in determining the entanglement degree between polymer chains. Solutions at low concentrations do not allow polymer chains to entangle leading the viscoeslasticity od the solution dependent only on individual polymer chains. As the polymer concentration increases, the chains overlap and become entangled. The concentration at which the entanglement initially takes place is the critical concentration $c^*$. Concentrations above the critical concentration $c^*$ generate a fast increase in chain entanglement. This rapid change in chain entanglement is translated into a fast increase in the viscoelasticity of the solution. Figure \ref{fig:concentrationViscosityPlotExplained} illustrates the relationship between polymer concentration and viscoelasticity. \cite{Burghelea2020, Gupta2005}

\begin{figure}[!th]
\centering
\includegraphics[scale=0.45]{./Figures/concentrationViscosityPlotExplained.png}
\decoRule
\caption[Selection of Polymer-Solvent Systems to Investigate in this Work]{Selection of Polymer-Solvent Systems to Investigate in this Work. \cite{Burghelea2020, Gupta2005, Han2019}}
\label{fig:concentrationViscosityPlotExplained}
\end{figure}

Electrospinning of smooth, continuous fibers require a polymer concentration higher than the critical concentration. As shown in Figure \ref{fig:concentrationViscosityPlotExplained}, the critical concentration can be estimated from the change in slope. \cite{Burghelea2020, Gupta2005, Han2019}
